---
output:
  pdf_document:
header-includes:
  - \thispagestyle{empty}
  - \usepackage{tabu}
  - \usepackage{booktabs}
---

```{r, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
#Load all the packages 
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(jpeg)
library(ggrepel)
library(knitr)
library(quantmod)
library(coinmarketcapr)
library(httr)
library(jsonlite)
library(scales)
library(kableExtra)
library(tinytex)
```


<!-- Data input -->

```{r, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
# Read the Excel file and get sheet names
excel_file <- params[["excel_file"]]
sheet_names <- excel_sheets(excel_file)

# Read each sheet into a data frame
data_list <- lapply(sheet_names, function(sheet) {
  read_excel(excel_file, sheet = sheet)
})

# Extract the "investors" sheet and filter by investor ID
investors <- data_list[[1]]
investor_id <- params[["ID"]]
filtered_data <- investors %>%
  filter(ID == investor_id)

# Access the investor's name
investor_name <- filtered_data$name
investor_lastname <- filtered_data$last_name

# Extract the "total_balance" sheet and filter by investor ID
total_balance <- data_list[[2]]

# Extract the "variable_income" sheet and filter by investor ID
variable_income <- data_list[[3]]

# Extract the "fixed_income" sheet and filter by investor ID
fixed_income <- data_list[[4]]

#-----------------------------------------------------------------------------------------------------
# BTC PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("BTC-USD",warnings = FALSE, auto.assign = TRUE)
BTC <- `BTC-USD`

# Get the last price
BTC_last_close_price <- as.numeric(tail(BTC$`BTC-USD.Close`, 1))

# Get the price 90 days ago
BTC_price_90_days_ago <- as.numeric(BTC$`BTC-USD.Close`[length(BTC$`BTC-USD.Close`) - 90])

# Calculate the percentage change
BTC_change <- round((BTC_last_close_price - BTC_price_90_days_ago) / BTC_price_90_days_ago, 4)
BTC_change <- percent(BTC_change)

#Calculate the BTC returns
BTC_return = diff(log(BTC$`BTC-USD.Close`))
BTC_return = BTC_return [-1]

# BNB PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("BNB-USD",warnings = FALSE, auto.assign = TRUE)
BNB <- `BNB-USD`

# Get the last price
BNB_last_close_price <- as.numeric(tail(BNB$`BNB-USD.Close`, 1))

# Get the price 90 days ago
BNB_price_90_days_ago <- as.numeric(BNB$`BNB-USD.Close`[length(BNB$`BNB-USD.Close`) - 90])

# Calculate the percentage change
BNB_change <- round((BNB_last_close_price - BNB_price_90_days_ago) / BNB_price_90_days_ago, 4)
BNB_change <- percent(BNB_change)

#Calculate the BNB returns
BNB_return = diff(log(BNB$`BNB-USD.Close`))
BNB_return = BNB_return [-1]

# CHZ PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("CHZ-USD",warnings = FALSE, auto.assign = TRUE)
CHZ <- `CHZ-USD`

# Get the last price 
CHZ_last_close_price <- as.numeric(tail(CHZ$`CHZ-USD.Close`, 1))

# Get the price 90 days ago
CHZ_price_90_days_ago <- as.numeric(CHZ$`CHZ-USD.Close`[length(CHZ$`CHZ-USD.Close`) - 90])

# Calculate the percentage change
CHZ_change <- round((CHZ_last_close_price - CHZ_price_90_days_ago) / CHZ_price_90_days_ago, 4)
CHZ_change <- percent(CHZ_change)

#Calculate the CHZ returns
CHZ_return = diff(log(CHZ$`CHZ-USD.Close`))
CHZ_return = CHZ_return [-1]

# ROSE PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("ROSE-USD",warnings = FALSE, auto.assign = TRUE)
ROSE <- `ROSE-USD`

# Get the last price 
ROSE_last_close_price <- as.numeric(tail(ROSE$`ROSE-USD.Close`, 1))

# Get the price 90 days ago
ROSE_price_90_days_ago <- as.numeric(ROSE$`ROSE-USD.Close`[length(ROSE$`ROSE-USD.Close`) - 90])

# Calculate the percentage change
ROSE_change <- round((ROSE_last_close_price - ROSE_price_90_days_ago) / ROSE_price_90_days_ago, 4)
ROSE_change <- percent(ROSE_change)

#Calculate the ROSE returns
ROSE_return = diff(log(ROSE$`ROSE-USD.Close`))
ROSE_return = ROSE_return [-1]

# WOO PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("WOO-USD",warnings = FALSE, auto.assign = TRUE)
WOO <- `WOO-USD`

# Get the last price 
WOO_last_close_price <- as.numeric(tail(`WOO-USD`$`WOO-USD.Close`, 1))

# Get the price 90 days ago
WOO_price_90_days_ago <- as.numeric(`WOO-USD`$`WOO-USD.Close`[length(`WOO-USD`$`WOO-USD.Close`) - 90])

# Calculate the percentage change
WOO_change <- round((WOO_last_close_price - WOO_price_90_days_ago) / WOO_price_90_days_ago, 4)
WOO_change <- percent(WOO_change)

#Calculate the WOO returns
WOO_return = diff(log(WOO$`WOO-USD.Close`))
WOO_return = WOO_return [-1]

# CRO PRICES
options("getSymbols.warning4.0" = TRUE)
options("getSymbols.yahoo.warning" = TRUE)
getSymbols("CRO-USD",warnings = FALSE, auto.assign = TRUE)
CRO <- `CRO-USD`

# Get the last price 
CRO_last_close_price <- as.numeric(tail(`CRO-USD`$`CRO-USD.Close`, 1))

# Get the price 90 days ago
CRO_price_90_days_ago <- as.numeric(`CRO-USD`$`CRO-USD.Close`[length(`CRO-USD`$`CRO-USD.Close`) - 90])

# Calculate the percentage change
CRO_change <- round((CRO_last_close_price - CRO_price_90_days_ago) / CRO_price_90_days_ago, 4)
CRO_change <- percent(CRO_change)

#Calculate the CRO returns
CRO_return = diff(log(CRO$`CRO-USD.Close`))
CRO_return = CRO_return [-1]

# AITECH PRICES
AITECH <- 0.020865

# Calculate the percentage change
AITECH_change <- percent(0)

#Calculate the AITECH returns
AITECH_return <- 0

# Read the CSV file
LUNA <- read.csv("C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/LUNA_price.csv")

# Get the last price 
LUNA_last_close_price <- tail(LUNA$close, 1)

# Get the price 90 days ago
LUNA_price_90_days_ago <- LUNA$close[length(LUNA$close) - 90]

# Calculate the percentage change
LUNA_change <- round((LUNA_last_close_price - LUNA_price_90_days_ago) / LUNA_price_90_days_ago, 4)
LUNA_change <- percent(LUNA_change)

#Calculate the LUNA returns
LUNA_return = diff(log(LUNA$close))
LUNA_return = LUNA_return [-1]

# AITECH PRICES
USD <- 1

# Calculate the percentage change
USD_change <- percent(0)

#Calculate the USD returns
USD_return <- 0

# AITECH PRICES
USD_ICO <- 1

# Calculate the percentage change
USD_ICO_change <- percent(0)

#Calculate the USD_ICO returns
USD_ICO_return <- 0

# Create the prices data frame
prices <- data.frame(
  Asset = c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Solidus Ai Tech", "Terra", "Digital Dolar", "ICO Digital Dolar"),
  Ticker_Symbol = c("BTC", "BNB", "CHZ", "ROSE", "WOO", "CRO", "AITECH", "LUNA", "USD", "USD_ICO"),
  Value = NA
)

# Create a data frame for the changes
changes <- data.frame(
  Asset = c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Solidus Ai Tech", "Terra", "Digital Dolar", "ICO Digital Dolar"),
  Ticker_Symbol = c("BTC", "BNB", "CHZ", "ROSE", "WOO", "CRO", "AITECH", "LUNA", "USD", "USD_ICO"),
  Change_3months = c(BTC_change, BNB_change, CHZ_change, ROSE_change, WOO_change, CRO_change, AITECH_change, LUNA_change, USD_change, USD_ICO_change)
)

# Assign the most recent price for each asset
prices$Value[prices$Asset == "Bitcoin"] <- as.numeric(format(tail(BTC, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Binance Coin"] <- as.numeric(format(tail(BNB, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Chiliz"] <- as.numeric(format(tail(CHZ, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Oasis Network"] <- as.numeric(format(tail(`ROSE-USD`, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "WOO Network"] <- as.numeric(format(tail(`WOO-USD`, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Cronos"] <- as.numeric(format(tail(`CRO-USD`, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Solidus Ai Tech"] <- as.numeric(format(tail(AITECH, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Terra"] <- as.numeric(format(tail(LUNA, 1), digits = 3, scientific = FALSE))
prices$Value[prices$Asset == "Digital Dolar"] <- USD
prices$Value[prices$Asset == "ICO Digital Dolar"] <- USD_ICO
```



<!-- Cover Page ------------------------------------------------------------------------------------------------------------>

\pagenumbering{arabic}

\begin{center}

\textcolor[HTML]{C7A61F}{\rule{0.5\linewidth}{2pt}}

\vspace{4cm}

\includegraphics[width=6cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}

\vspace{2.5cm}

\fontsize{28}{28}\selectfont
\textbf{Monthly Investment Report}

\vspace{2cm}

\fontsize{24}{24}\selectfont
\textbf{`r investor_name` `r investor_lastname`}

\fontsize{24}{24}\selectfont
\textbf{`r params$ID`}

\vspace{2.5cm}

\fontsize{18}{18}\selectfont
Prepared by: José Ramón Cobos

\fontsize{18}{18}\selectfont
`r format(Sys.time(), '%d, %B, %Y')`

\vspace{2.5cm}

\textcolor[HTML]{C7A61F}{\rule{0.5\linewidth}{2pt}}

\end{center}



<!-- Executive Summary ----------------------------------------------------------------------------------------------->

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{20}{18}\selectfont
\textbf{1. Executive Summary}

\vspace{0.2cm}

\fontsize{14}{16}\selectfont
Z Financial Growth is pleased to present the executive summary for the monthly investment report. This report provides an overview of the investment performance and activities for the month of `r params$month`, `r params$year`.

\vspace{0.6cm}

\fontsize{17}{12}\selectfont
\textbf{Investment Summary}

\vspace{0.2cm}

\fontsize{14}{14}\selectfont
\textbf{Introduction:}

\fontsize{14}{16}\selectfont
In `r params$month` `r params$year`, Z Financial Growth continued to manage client capital, focusing on cryptocurrency investments. With a firm commitment to long-term prospects, we prioritize projects that build stable and profitable ecosystems, rather than fixating on short-term price fluctuations.

\vspace{0.3cm}

\fontsize{14}{14}\selectfont
\textbf{Investment philosophy:}

\fontsize{14}{16}\selectfont
Our philosophy revolves around supporting blockchain-based companies with strong fundamentals, innovative technology and profitable ecosystems. We prioritize projects that bring tangible value to users and stakeholders, relying less on market sentiment.

\vspace{0.3cm}

\fontsize{14}{14}\selectfont
\textbf{Thorough analysis:}

\fontsize{14}{16}\selectfont
Each investment decision undergoes thorough analysis, assessing long-term prospects and the potential for transformative solutions. Our due diligence takes into account factors such as technology, market demand and adaptability to shape competitive sectors.

\vspace{0.3cm}

\fontsize{14}{14}\selectfont
\textbf{Commitment to the future:}

\fontsize{14}{16}\selectfont
Going forward, we remain dedicated to our investment philosophy, emphasizing patient and prudent investments in projects that shape the future of blockchain technology. Our goal is to drive lasting value for clients while fostering industry advancements.

\vspace{0.3cm}

\fontsize{14}{14}\selectfont
\textbf{Conclusion:}

\fontsize{14}{16}\selectfont
Z Financial Growth's approach to cryptocurrency capital management focuses on long-term growth. We prioritize projects with strong fundamentals, innovative technology and the potential for profitable ecosystems. Through thorough analysis and unwavering commitment, we shape the future of blockchain technology, ensuring the success of our clients' financial endeavors.

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{17}{12}\selectfont
\textbf{Portfolio Holdings}

\vspace{0.2cm}

\fontsize{14}{16}\selectfont
Z Financial Growth maintained a diversified portfolio across various cryptocurrencies to ensure risk management and capture potential growth opportunities. The portfolio holdings for `r params$month`, `r params$year` included:

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.keep = 'all', fig.width = 5}
#Dreate the quantity data frame
quantity <- total_balance %>%
    filter(ID == investor_id) %>%
    select(matches(prices$Ticker_Symbol))

quantity_organized <- quantity %>%
  pivot_longer(everything(), names_to = "Asset", values_to = "Quantity") %>%
  select(Asset, Quantity)%>%
  mutate(Asset = gsub("\\$", "", Asset),
         Quantity = round(Quantity, 2))

# Create the per_asset data frame
per_asset <- data.frame(
  Asset = prices$Asset,
  Ticker_Symbol = prices$Ticker_Symbol,
  Market_value = ifelse(prices$Value < 1, round(prices$Value, 3), round(prices$Value, 0))
)

# Merge per_asset and quantity_organized by Ticker_Symbol and Asset
per_asset <- merge(per_asset, quantity_organized, by.x = "Ticker_Symbol", by.y = "Asset")

# Merge per_asset and quantity_organized by Ticker_Symbol and Asset
per_asset <- merge(per_asset, select(changes, Ticker_Symbol, Change_3months), by = "Ticker_Symbol")

#create total value
per_asset$Total_Value <- round(per_asset$Market_value * per_asset$Quantity, 2)

# Rearrange the columns
per_asset <- per_asset[, c("Asset", "Ticker_Symbol", "Market_value", "Quantity", "Total_Value", "Change_3months")]

#Filtering the top 4 assets
top4_assets <- per_asset %>%
  arrange(desc(Total_Value)) %>%
  head(4) %>%
  mutate(Allocation = Total_Value / sum(Total_Value))

# Calculate the total value of top 4 assets
top4_total_value <- sum(top4_assets$Total_value)

# Create the others data frame
others <- per_asset %>%
  filter(!(Asset %in% top4_assets$Asset)) %>%
  summarise(
    Asset = "Others",
    Ticker_Symbol = "Others",
    Market_value = NA,
    Quantity = NA,
    Total_Value = sum(Total_Value) - top4_total_value,
    Change_3months = NA,
  ) %>%
  mutate(Allocation = Total_Value / sum(per_asset$Total_Value - top4_total_value))

#Joining the top4_assets and the others assets
portfolio_holdings <- bind_rows(top4_assets, others)

# Extract unique Asset values from top4_assets and add "Others" separately
top4_asset_levels <- top4_assets$Asset
asset_levels <- c(top4_assets$Asset, "Others")

# Convert Asset column to factor with desired order
portfolio_holdings$Asset <- factor(portfolio_holdings$Asset, levels = asset_levels)

# Plot the pie chart
positions <- portfolio_holdings %>% 
  mutate(csum = rev(cumsum(rev(Allocation))), 
         pos = Allocation/2 + lead(csum, 1),
         pos = if_else(is.na(pos), Allocation/2, pos))

pie_chart <- ggplot(portfolio_holdings, aes(x = "", y = Allocation, fill = Asset)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  labs(fill = "Asset", x = NULL, y = NULL) +
  theme_void() +
  geom_label_repel(data = positions,
                   aes(y = pos, label = paste0(round(Allocation * 100), "%")),
                   size = 4, nudge_x = 0.3, show.legend = FALSE)

pie_chart
```

\fontsize{14}{16}\selectfont
The portfolio holdings were prudently allocated based on thorough analysis of each cryptocurrency's potential for growth and risk.


<!-- Investment Overview ------------------------------------------------------------------------------->

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{20}{18}\selectfont
\textbf{2. Investment Overview}

\vspace{0.75cm}

\fontsize{17}{12}\selectfont
\textbf{Portfolio Summary}


<!-- Performing some calculations and showing general information about the portfolio -->
```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.keep = 'all'}
# Calculations
initial_investment <- round(investors$Quantity[investors$ID == investor_id], 2)
present_value <- round(total_balance$`Total $`[total_balance$ID == investor_id], 2)
withdrawals <- round(investors$Withdrawals[investors$ID == investor_id], 2)
result <- present_value + withdrawals - initial_investment

# Text part on the left
text_output <- paste(
  "Initial investment: ", format(initial_investment, big.mark = "."), "$\n",
  "Withdrawals: ", format(withdrawals, big.mark = "."), "$\n",
  "Present Value: ", format(present_value, big.mark = "."), "$\n",
  "Result: ", format(result, big.mark = "."), "$\n"
)

# Create the data frame
data_plot_1 <- data.frame(
  Label = factor(c("Initial Investment", "Withdrawals", "Present Value", "Result"),
                 levels = c("Initial Investment", "Withdrawals", "Present Value", "Result")),
  Value = c(initial_investment, withdrawals, present_value, result)
)

# Create the bar plot using ggplot
plot_output <- ggplot(data_plot_1, aes(x = Label, y = Value)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.8, color = "black") +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    panel.grid.major = element_blank(),
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1)
)
```

```{r, echo = FALSE, results = 'hide', message = FALSE, fig.keep = 'all', fig.width = 6, fig.height = 3.5}
# Combine the text and plot outputs using grid.arrange
grid_output <- grid.arrange(textGrob(text_output), plot_output, ncol = 2)

# Print the grid output
print(grid_output)
```

\vspace{1.5cm}

\fontsize{17}{12}\selectfont
\textbf{Overviw Per Asset}

\vspace{1cm}

```{r, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
#Creating the table data frame
top4_table <- top4_assets
top4_table$Total_Value <- paste0(top4_table$Total_Value, " $")
top4_table$Allocation <- percent(top4_table$Allocation)
top4_table$Market_value <- ifelse(top4_table$Market_value >= 1, round(top4_table$Market_value, 0), round(top4_table$Market_value, 3))
top4_table$Quantity <- ifelse(top4_table$Quantity >= 100, round(top4_table$Quantity, 0), round(top4_table$Quantity, 3))

# Generate the table
kbl(top4_table,
    booktabs = TRUE,
    col.names = c("Asset", "Symbol", "Market Value", "Quantity", "Total Value", "3M Change", "Allocation"),
    align = "ccc") %>%
  kable_styling(full_width = TRUE,
                font_size = 9) %>%
  row_spec(0, bold = TRUE)
```

\newpage

```{r, echo = FALSE, results = "hide", message = FALSE, warning = FALSE}
#mean of the return per asset: 
BTC_mean_return <- mean(BTC_return, na.rm = TRUE)
BNB_mean_return <- mean(BNB_return, na.rm = TRUE)
CHZ_mean_return <- mean(CHZ_return, na.rm = TRUE)
ROSE_mean_return <- mean(ROSE_return, na.rm = TRUE)
WOO_mean_return <- mean(WOO_return, na.rm = TRUE)
CRO_mean_return <- mean(CRO_return, na.rm = TRUE)
AITECH_mean_return <- mean(AITECH_return, na.rm = TRUE)
LUNA_mean_return <- mean(LUNA_return, na.rm = TRUE)
USD_mean_return <- mean(USD_return, na.rm = TRUE)
USD_ICO_mean_return <- mean(USD_ICO_return, na.rm = TRUE)

#Creatingn a data frame for the mean returns
mean_returns <- data.frame(
  Asset = c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Solidus Ai Tech", "Terra", "Digital Dolar", "ICO Digital Dolar"),
  Ticker_Symbol = c("BTC", "BNB", "CHZ", "ROSE", "WOO", "CRO", "AITECH", "LUNA", "USD", "USD_ICO"),
  mean_return = c(BTC_mean_return, BNB_mean_return, CHZ_mean_return, ROSE_mean_return, WOO_mean_return, CRO_mean_return, AITECH_mean_return, LUNA_mean_return, USD_mean_return, USD_ICO_mean_return)
)

# Standart deviation 
BTC_sd <- sd(BTC_return, na.rm = TRUE) 
BNB_sd <- sd(BNB_return, na.rm = TRUE) 
CHZ_sd <- sd(CHZ_return, na.rm = TRUE) 
ROSE_sd <- sd(ROSE_return, na.rm = TRUE) 
WOO_sd <- sd(WOO_return, na.rm = TRUE) 
CRO_sd <- sd(CRO_return, na.rm = TRUE) 
AITECH_sd <- sd(AITECH_return, na.rm = TRUE) 
LUNA_sd <- sd(LUNA_return, na.rm = TRUE) 
USD_sd <- sd(USD_return, na.rm = TRUE) 
USD_sd <- sd(USD_ICO_return, na.rm = TRUE) 

#Creatingn a data frame for the sd
sd_df <- data.frame(
  Asset = c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Solidus Ai Tech", "Terra", "Digital Dolar", "ICO Digital Dolar"),
  Ticker_Symbol = c("BTC", "BNB", "CHZ", "ROSE", "WOO", "CRO", "AITECH", "LUNA", "USD", "USD_ICO"),
  standard_deviation = c(BTC_sd, BNB_sd, CHZ_sd, ROSE_sd, WOO_sd, CRO_sd, AITECH_sd, LUNA_sd, USD_sd, USD_sd)
)

# Percentiles
tauseq = seq(0,1,.1) # generate sequence of numbers that will be used as quantiles

BTC_percentiles <- quantile(BTC_return, tauseq, na.rm = TRUE)
BNB_percentiles <- quantile(BNB_return, tauseq, na.rm = TRUE)
CHZ_percentiles <- quantile(CHZ_return, tauseq, na.rm = TRUE)
ROSE_percentiles <- quantile(ROSE_return, tauseq, na.rm = TRUE)
WOO_percentiles <- quantile(WOO_return, tauseq, na.rm = TRUE)
CRO_percentiles <- quantile(CRO_return, tauseq, na.rm = TRUE)
AITECH_percentiles <- quantile(AITECH_return, tauseq, na.rm = TRUE)
LUNA_percentiles <- quantile(LUNA_return, tauseq, na.rm = TRUE)
USD_percentiles <- quantile(USD_return, tauseq, na.rm = TRUE)
USD_ICO_percentiles <- quantile(USD_ICO_return, tauseq, na.rm = TRUE)

# estimate kernel density & plot the estimated density 
BTC_density = density(BTC_return, na.rm = TRUE) 
BNB_density = density(BNB_return, na.rm = TRUE) 
CHZ_density = density(CHZ_return, na.rm = TRUE) 
ROSE_density = density(ROSE_return, na.rm = TRUE) 
WOO_density = density(WOO_return, na.rm = TRUE) 
CRO_density = density(CRO_return, na.rm = TRUE) 
LUNA_density = density(LUNA_return, na.rm = TRUE) 

#Calculations only for the first asset of the top4_assets
first_asset <- top4_assets[1,1]

first_mean <- paste0(round(mean_returns[mean_returns$Asset == first_asset, 3] * 100, 2), " %")
first_sd <- paste0(round(sd_df[sd_df$Asset == first_asset, 3] * 100, 2), " %")

first_asset_return <- switch(first_asset,
                             "Bitcoin" = BTC_return,
                             "Binance Coin" = BNB_return,
                             "Chiliz" = CHZ_return,
                             "Oasis Network" = ROSE_return,
                             "WOO Network" = WOO_return,
                             "Cronos" = CRO_return,
                             "Solidus Ai Tech" = AITECH_return,
                             "Terra" = LUNA_return,
                             "Digital Dolar" = USD_return,
                             "ICO Digital Dolar" = USD_ICO_return)

first_asset_quantiles_df <- data.frame(
  Deciles = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
  Return = paste0(round(quantile(first_asset_return, tauseq, na.rm = TRUE) * 100, 2), " %")
)

first_asset_quantiles_table <- kbl(first_asset_quantiles_df,
                                   booktabs = TRUE,
                                   col.names = c("Deciles", "Return"),
                                   align = "ccc") %>%
  kable_styling(full_width = TRUE,
                font_size = 10) %>%
  row_spec(0, bold = TRUE)

if (first_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  first_asset_density <- density(first_asset_return, na.rm = TRUE)
} else {
  first_asset_density <- NULL
}

#Calculations only for the second asset of the top4_assets
second_asset <- top4_assets[2,1]

second_mean <- paste0(round(mean_returns[mean_returns$Asset == second_asset, 3] * 100, 2), " %")
second_sd <- paste0(round(sd_df[sd_df$Asset == second_asset, 3] * 100, 2), " %")

second_asset_return <- switch(second_asset,
                             "Bitcoin" = BTC_return,
                             "Binance Coin" = BNB_return,
                             "Chiliz" = CHZ_return,
                             "Oasis Network" = ROSE_return,
                             "WOO Network" = WOO_return,
                             "Cronos" = CRO_return,
                             "Solidus Ai Tech" = AITECH_return,
                             "Terra" = LUNA_return,
                             "Digital Dolar" = USD_return,
                             "ICO Digital Dolar" = USD_ICO_return)

second_asset_quantiles_df <- data.frame(
  Deciles = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
  Return = paste0(round(quantile(second_asset_return, tauseq, na.rm = TRUE) * 100, 2), " %")
)

second_asset_quantiles_table <- kbl(second_asset_quantiles_df,
                                   booktabs = TRUE,
                                   col.names = c("Deciles", "Return"),
                                   align = "ccc") %>%
  kable_styling(full_width = TRUE,
                font_size = 10) %>%
  row_spec(0, bold = TRUE)

if (second_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  second_asset_density <- density(second_asset_return, na.rm = TRUE)
} else {
  second_asset_density <- NULL
}

#Calculations only for the third asset of the top4_assets
third_asset <- top4_assets[3,1]

third_mean <- paste0(round(mean_returns[mean_returns$Asset == third_asset, 3] * 100, 2), " %")
third_sd <- paste0(round(sd_df[sd_df$Asset == third_asset, 3] * 100, 2), " %")

third_asset_return <- switch(third_asset,
                             "Bitcoin" = BTC_return,
                             "Binance Coin" = BNB_return,
                             "Chiliz" = CHZ_return,
                             "Oasis Network" = ROSE_return,
                             "WOO Network" = WOO_return,
                             "Cronos" = CRO_return,
                             "Solidus Ai Tech" = AITECH_return,
                             "Terra" = LUNA_return,
                             "Digital Dolar" = USD_return,
                             "ICO Digital Dolar" = USD_ICO_return)

third_asset_quantiles_df <- data.frame(
  Deciles = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
  Return = paste0(round(quantile(third_asset_return, tauseq, na.rm = TRUE) * 100, 2), " %")
)

third_asset_quantiles_table <- kbl(third_asset_quantiles_df,
                                   booktabs = TRUE,
                                   col.names = c("Deciles", "Return"),
                                   align = "ccc") %>%
  kable_styling(full_width = TRUE,
                font_size = 10) %>%
  row_spec(0, bold = TRUE)

if (third_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  third_asset_density <- density(third_asset_return, na.rm = TRUE)
} else {
  third_asset_density <- NULL
}

#Calculations only for the fourth asset of the top4_assets
fourth_asset <- top4_assets[4,1]

fourth_mean <- paste0(round(mean_returns[mean_returns$Asset == fourth_asset, 3] * 100, 2), " %")
fourth_sd <- paste0(round(sd_df[sd_df$Asset == fourth_asset, 3] * 100, 2), " %")

fourth_asset_return <- switch(fourth_asset,
                             "Bitcoin" = BTC_return,
                             "Binance Coin" = BNB_return,
                             "Chiliz" = CHZ_return,
                             "Oasis Network" = ROSE_return,
                             "WOO Network" = WOO_return,
                             "Cronos" = CRO_return,
                             "Solidus Ai Tech" = AITECH_return,
                             "Terra" = LUNA_return,
                             "Digital Dolar" = USD_return,
                             "ICO Digital Dolar" = USD_ICO_return)

fourth_asset_quantiles_df <- data.frame(
  Deciles = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100),
  Return = paste0(round(quantile(fourth_asset_return, tauseq, na.rm = TRUE) * 100, 2), " %")
)

fourth_asset_quantiles_table <- kbl(fourth_asset_quantiles_df,
                                   booktabs = TRUE,
                                   col.names = c("Deciles", "Return"),
                                   align = "ccc") %>%
  kable_styling(full_width = TRUE,
                font_size = 10) %>%
  row_spec(0, bold = TRUE)

if (fourth_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  fourth_asset_density <- density(fourth_asset_return, na.rm = TRUE)
} else {
  fourth_asset_density <- NULL
}

```

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{17}{12}\selectfont
\textbf{Investment Per Asset - Detailed Historical Data}

\vspace{0.75cm}

\fontsize{15}{12}\selectfont
\textbf{`r first_asset`}

\vspace{0.5cm}

\fontsize{14}{16}\selectfont
\textbf{Average Return:}  `r first_mean`

\textbf{Variation:}  `r first_sd`

\textbf{Deciles:}

`r first_asset_quantiles_table`

\textbf{Density:}

```{r, echo = FALSE, results = "hide", message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4, fig.align = "center"}
if (first_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  plot(first_asset_density, main = "", xlab = "")
} else {
  first_asset_density <- NULL
}
```

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{15}{12}\selectfont
\textbf{`r second_asset`}

\vspace{0.5cm}

\fontsize{14}{16}\selectfont
\textbf{Average Return:}  `r second_mean`

\textbf{Variation:}  `r second_sd`

\textbf{Deciles:}

`r second_asset_quantiles_table`

\textbf{Density:}

```{r, echo = FALSE, results = "hide", message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4, fig.align = "center"}
if (second_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  plot(second_asset_density, main = "", xlab = "")
} else {
  second_asset_density <- NULL
}
```

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{15}{12}\selectfont
\textbf{`r third_asset`}

\vspace{0.5cm}

\fontsize{14}{16}\selectfont
\textbf{Average Return:}  `r third_mean`

\textbf{Variation:}  `r third_sd`

\textbf{Deciles:}

`r third_asset_quantiles_table`

\textbf{Density:}

```{r, echo = FALSE, results = "hide", message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4, fig.align = "center"}
if (third_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  plot(third_asset_density, main = "", xlab = "")
} else {
  third_asset_density <- NULL
}
```

\newpage

\begin{minipage}[t][0pt]{\textwidth}
    \vspace{-2 cm}\hspace{-2 cm}
    \includegraphics[width = 3.5cm]{C:/Users/pepec/Desktop/estudios/master/Report_Generator/Inst/logo.jpg}
\end{minipage}

\fontsize{15}{12}\selectfont
\textbf{`r fourth_asset`}

\vspace{0.5cm}

\fontsize{14}{16}\selectfont
\textbf{Average Return:}  `r fourth_mean`

\textbf{Variation:}  `r fourth_sd`

\textbf{Deciles:}

`r fourth_asset_quantiles_table`

\textbf{Density:}

```{r, echo = FALSE, results = "hide", message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4, fig.align = "center"}
if (fourth_asset %in% c("Bitcoin", "Binance Coin", "Chiliz", "Oasis Network", "WOO Network", "Cronos", "Terra")) {
  plot(fourth_asset_density, main = "", xlab = "")
} else {
  fourth_asset_density <- NULL
}
```




